Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
Update paper.tex

\todo{The overal performance score.}

@@

\todo{Analysis}

@@

Since we decompose two networks into two sets of internally disjoint clusters, each subclass will fall into exactly two clusters from separate models.
In other word, the encoding for a subclass is a two-hot encoding.
\todo{This means that the assembly problem can be solved with more efficient algorithms.}

@@

\section{Conclusion}
The conclusion \dots

>>>>

@@

@@

Since we decompose two networks into two sets of internally disjoint clusters, each subclass will fall into exactly two clusters from separate models.
In other word, the encoding for a subclass is a two-hot encoding.
This means that the assembly problem can be solved with more efficient algorithms.

@@

\section{Conclusion}
In this work, to develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers. 
And we formulate the choice of these classifiers into a search problem. 
We implement this framework based on CDRP method for image classification task. 
In our experiment, we successfully reduce about $90\%$ computing consumption by pruning $90\%$ channels in the network while reach a high classification accuracy.

In future work, we may take the accuracy of classifiers into account so that we can choose binary-classifiers with performance score, which can help to achieve a higher accuracy. 
Furthermore, we can design more efficient search algorithm according to the characteristics of subclasses, for example, like each subclass only fall into two clusters as shown in  \cref{fig:network-venn}.
